---
title: "Research report simulations"
author: 
  - Thom Volker
date: "`r format(Sys.time(), '%B %d, %Y')`"
mainfont: Arial
fontsize: 12pt
urlcolor: blue
output: 
  html_document:
    toc: true
    toc_depth: 1
    toc_float: true
    number_sections: true
    code_folding: hide
    df_print: paged
    theme: paper
    highlight: pygments
    latexengine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, include = FALSE}
library(tidyverse)
library(magrittr)
```

# Simulation 1

```{r, include = F}
load("../simulations/01_sample_size_equal.RData")
```

In this simulation, I created data according to a multivariate normal distribution, where all variables had variance $\sigma^2 = 1$. The predictor variables $X$ with dimensions $(n \times k)$ with $n \in \{`r unique(output$n)`\}$ and $k = 4$ were correlated with $\rho = 0.3$. The outcome variable $Y$, and the ratio of the regression coefficients equals $\beta_4 = 4\beta_1, \beta_3 = 3\beta_1, \beta_2 = 2\beta_1$, with the exact size depending on the proportion explained variance $R^2$ of the regression model.

The hypothesis of interest was 
$$
H_i: \beta_1 < \beta_2 < \beta_3 < \beta_4,
$$
and was evaluated against an unconstrained hypothesis
$$
H_u: \beta_1, \beta_2, \beta_3, \beta_4.
$$

```{r}
output <- output %>%
  mutate(bf_u  = map(fit,  ~c(.x[,7], unconstrained = 1)),
         bf_h1 = map_dbl(bf_u, ~.x[1]),
         pmp_u = map(bf_u, ~.x / sum(.x)),
         r2 = paste0("R^2: ", r2))

output %>%
  group_by(n, r2, model) %>%
  summarize(bf_h1 = mean(bf_h1), .groups = "drop") %>%
  ggplot(mapping = aes(x = n, y = bf_h1, col = model)) +
  geom_line() +
  geom_hline(yintercept = 1, col = "grey", size = 1) +
  scale_color_brewer(palette = "Set1") +
  facet_wrap(~r2, labeller = label_parsed) +
  theme_minimal() +
  labs(y = expression(BF["H"["i,u"]]),
       x = "Sample size",
       title = "Individual study Bayes Factor")

hypnames <- c("Hi", "Complement", "Unconstrained")

output %>%
  mutate(bf_u = map(bf_u, ~as_tibble(matrix(.x, 
                                            ncol = 3, 
                                            dimnames = list(NULL, 
                                                            hypnames))))) %>%
  unnest(bf_u) %>%
  mutate(Hi = ifelse(Hi > Unconstrained, 1, 0)) %>%
  group_by(n, r2, model) %>%
  summarize(thr = mean(Hi), .groups = "drop") %>%
  ggplot(aes(x = n, y = thr, col = model)) +
  geom_line() +
  facet_wrap(~r2, labeller = label_parsed) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  labs(y = "Hypothesis selection rates",
       x = "Sample size",
       title = "Individual study true hypothesis selection rate")

output %>%
  group_by(nsim, n, r2) %>%
  summarize(bf_h1 = prod(bf_h1), .groups = "drop") %>%
  ggplot(aes(x = as.factor(n), y = log(bf_h1), fill = as.factor(n))) +
  geom_boxplot() +
  geom_hline(yintercept = 0, col = "grey", size = 1) +
  facet_wrap(~r2, labeller = label_parsed) +
  scale_fill_brewer(palette = "Set2") +
  theme_minimal() +
  labs(y = expression(log~BF["H"["i,u"]]),
       x = "Sample size",
       title = "Combined Bayes Factor") +
  theme(legend.position = "none")

output %>%
  mutate(bf_u = map(bf_u, ~as_tibble(matrix(.x,
                                            ncol = 3,
                                            dimnames = list(NULL,
                                                            hypnames))))) %>%
  unnest(bf_u) %>%
  group_by(nsim, n, r2) %>%
  summarise(across(c(Hi, Complement, Unconstrained), prod), .groups = "drop") %>%
  mutate(Hi = ifelse(Hi > Unconstrained, 1, 0),
         Unconstrained = ifelse(Unconstrained > Hi, 1, 0)) %>%
  group_by(n, r2) %>%
  summarize(thr = mean(Hi), .groups = "drop") %>%
  ggplot(aes(x = n, y = thr, col = r2)) +
  geom_line() +
  scale_color_brewer(palette = "Set1", labels = scales::parse_format()) +
  theme_minimal() +
  labs(y = "True hypothesis rate",
       x = "Sample size",
       title = "True hypothesis rate of hypothesis of interest versus unconstrained")
```

# Simulation 2

Simulation 2 is basically a replication of simulation 1, with as the only difference that in all "meta-studies" there is a single study randomly selected to have a sample size of $n = 25$. So again, the hypothesis of interest that is evaluated is
$$
H_i: \beta_1 < \beta_2 < \beta_3 < \beta_4,
$$
relative to 
$$
H_u: \beta_1, \beta_2, \beta_3, \beta_4.
$$

```{r, include = F}
rm(list = ls())
load("../simulations/02_sample_size_underpowered.RData")
```

```{r}
output <- output %>%
  mutate(bf_u  = map(fit,  ~c(.x[,7], unconstrained = 1)),
         bf_h1 = map_dbl(bf_u, ~.x[1]),
         pmp_u = map(bf_u, ~.x / sum(.x)),
         r2 = paste0("R^2: ", r2))

output %>%
  group_by(n_initial, r2, model) %>%
  summarize(bf_h1 = mean(bf_h1), .groups = "drop") %>%
  ggplot(mapping = aes(x = n_initial, y = bf_h1, col = model)) +
  geom_line() +
  geom_hline(yintercept = 1, col = "grey", size = 1) +
  scale_color_brewer(palette = "Set1") +
  facet_wrap(~r2, labeller = label_parsed) +
  theme_minimal() +
  labs(y = expression(BF["H"["i,u"]]),
       x = "Sample size",
       title = "Individual study Bayes Factor")

hypnames <- c("Hi", "Complement", "Unconstrained")

output %>%
  mutate(bf_u = map(bf_u, ~as_tibble(matrix(.x, 
                                            ncol = 3, 
                                            dimnames = list(NULL, 
                                                            hypnames))))) %>%
  unnest(bf_u) %>%
  mutate(Hi = ifelse(Hi > Unconstrained, 1, 0)) %>%
  group_by(n_initial, r2, model) %>%
  summarize(thr = mean(Hi), .groups = "drop") %>%
  ggplot(aes(x = n_initial, y = thr, col = model)) +
  geom_line() +
  facet_wrap(~r2, labeller = label_parsed) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  labs(y = "Hypothesis selection rates",
       x = "Sample size",
       title = "Individual study true hypothesis selection rate")

output %>%
  group_by(nsim, n_initial, r2) %>%
  summarize(bf_h1 = prod(bf_h1), .groups = "drop") %>%
  ggplot(aes(x = as.factor(n_initial), 
             y = log(bf_h1), 
             fill = as.factor(n_initial))) +
  geom_boxplot() +
  geom_hline(yintercept = 0, col = "grey", size = 1) +
  facet_wrap(~r2, labeller = label_parsed) +
  scale_fill_brewer(palette = "Set2") +
  theme_minimal() +
  labs(y = expression(log~BF["H"["i,u"]]),
       x = "Sample size",
       title = "Combined Bayes Factor") +
  theme(legend.position = "none")

output %>%
  mutate(bf_u = map(bf_u, ~as_tibble(matrix(.x,
                                            ncol = 3,
                                            dimnames = list(NULL,
                                                            hypnames))))) %>%
  unnest(bf_u) %>%
  group_by(nsim, n_initial, r2) %>%
  summarise(across(c(Hi, Complement, Unconstrained), prod), .groups = "drop") %>%
  mutate(Hi = ifelse(Hi > Unconstrained, 1, 0),
         Unconstrained = ifelse(Unconstrained > Hi, 1, 0)) %>%
  group_by(n_initial, r2) %>%
  summarize(thr = mean(Hi), .groups = "drop") %>%
  ggplot(aes(x = n_initial, y = thr, col = r2)) +
  geom_line() +
  scale_color_brewer(palette = "Set1", labels = scales::parse_format()) +
  theme_minimal() +
  labs(y = "True hypothesis rate",
       x = "Sample size",
       title = "True hypothesis rate of hypothesis of interest versus unconstrained")
```

# Simulation 3

Simulation 3 is an extension of simulation 1 in the sense that the number of predictor variables equals $k = 5$, bivariately correlated still with $\rho = 0.3$. The ratio of the regression coefficients now equalled $\beta_5 = 3\beta_1, \beta_4 = 2\beta_1, \beta_3 = \beta_2 = \beta_1$, and hence there are three regression coefficients of equal size.

The hypothesis of interest was
$$
H_i: \beta_1 > 0; \beta_2 > 0; \beta_3 > 0,
$$

evaluated against the unconstrained hypothesis
$$
H_u: \beta_1, \beta_2, \beta_3, \beta_4, \beta_5.
$$
Hence, not every regression coefficient is included in the hypothesis of interest (the predictors with the largest size are not included in the hypothesis of interest).


```{r, include = F}
rm(list = ls())
load("../simulations/03_separated_variables.RData")
```

```{r}
output <- output %>%
  mutate(bf_u  = map(fit,  ~c(.x[,7], unconstrained = 1)),
         bf_h1 = map_dbl(bf_u, ~.x[1]),
         pmp_u = map(bf_u, ~.x / sum(.x)),
         r2 = paste0("R^2: ", r2))

output %>%
  group_by(n, r2, model) %>%
  summarize(bf_h1 = mean(bf_h1), .groups = "drop") %>%
  ggplot(mapping = aes(x = n, y = bf_h1, col = model)) +
  geom_line() +
  geom_hline(yintercept = 1, col = "grey", size = 1) +
  scale_color_brewer(palette = "Set1") +
  facet_wrap(~r2, labeller = label_parsed) +
  theme_minimal() +
  labs(y = expression(BF["H"["i,u"]]),
       x = "Sample size",
       title = "Individual study Bayes Factor")

hypnames <- c("Hi", "Complement", "Unconstrained")

output %>%
  mutate(bf_u = map(bf_u, ~as_tibble(matrix(.x, 
                                            ncol = 3, 
                                            dimnames = list(NULL, 
                                                            hypnames))))) %>%
  unnest(bf_u) %>%
  mutate(Hi = ifelse(Hi > Unconstrained, 1, 0)) %>%
  group_by(n, r2, model) %>%
  summarize(thr = mean(Hi), .groups = "drop") %>%
  ggplot(aes(x = n, y = thr, col = model)) +
  geom_line() +
  facet_wrap(~r2, labeller = label_parsed) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  labs(y = "Hypothesis selection rates",
       x = "Sample size",
       title = "Individual study true hypothesis selection rate")

output %>%
  group_by(nsim, n, r2) %>%
  summarize(bf_h1 = prod(bf_h1), .groups = "drop") %>%
  ggplot(aes(x = as.factor(n), 
             y = log(bf_h1), 
             fill = as.factor(n))) +
  geom_boxplot() +
  geom_hline(yintercept = 0, col = "grey", size = 1) +
  facet_wrap(~r2, labeller = label_parsed) +
  scale_fill_brewer(palette = "Set2") +
  theme_minimal() +
  labs(y = expression(log~BF["H"["i,u"]]),
       x = "Sample size",
       title = "Combined Bayes Factor") +
  theme(legend.position = "none")

output %>%
  mutate(bf_u = map(bf_u, ~as_tibble(matrix(.x,
                                            ncol = 3,
                                            dimnames = list(NULL,
                                                            hypnames))))) %>%
  unnest(bf_u) %>%
  group_by(nsim, n, r2) %>%
  summarise(across(c(Hi, Complement, Unconstrained), prod), .groups = "drop") %>%
  mutate(Hi = ifelse(Hi > Unconstrained, 1, 0),
         Unconstrained = ifelse(Unconstrained > Hi, 1, 0)) %>%
  group_by(n, r2) %>%
  summarize(thr = mean(Hi), .groups = "drop") %>%
  ggplot(aes(x = n, y = thr, col = r2)) +
  geom_line() +
  scale_color_brewer(palette = "Set1", labels = scales::parse_format()) +
  theme_minimal() +
  labs(y = "True hypothesis rate",
       x = "Sample size",
       title = "True hypothesis rate of hypothesis of interest versus unconstrained")
```


# Simulation 4

Simulation 4 is exactly similar to simulation 3, except that now $\beta_1, \beta_2, \beta_3$ are combined into a single variable that is the sum of the three separate variables, which yields the hypothesis of interest
$$
H_i: \beta_{sum} > 0, 
$$
evaluated against
$$
H_u: \beta_{sum}, \beta_4, \beta_5.
$$


```{r, include = F}
rm(list = ls())
load("../simulations/04_combined_variable_sum.RData")
```

```{r}
output <- output %>%
  mutate(bf_u  = map(fit,  ~c(.x[,7], unconstrained = 1)),
         bf_h1 = map_dbl(bf_u, ~.x[1]),
         pmp_u = map(bf_u, ~.x / sum(.x)),
         r2 = paste0("R^2: ", r2))

output %>%
  group_by(n, r2, model) %>%
  summarize(bf_h1 = mean(bf_h1), .groups = "drop") %>%
  ggplot(mapping = aes(x = n, y = bf_h1, col = model)) +
  geom_line() +
  geom_hline(yintercept = 1, col = "grey", size = 1) +
  scale_color_brewer(palette = "Set1") +
  facet_wrap(~r2, labeller = label_parsed) +
  theme_minimal() +
  labs(y = expression(BF["H"["i,u"]]),
       x = "Sample size",
       title = "Individual study Bayes Factor")

hypnames <- c("Hi", "Complement", "Unconstrained")

output %>%
  mutate(bf_u = map(bf_u, ~as_tibble(matrix(.x, 
                                            ncol = 3, 
                                            dimnames = list(NULL, 
                                                            hypnames))))) %>%
  unnest(bf_u) %>%
  mutate(Hi = ifelse(Hi > Unconstrained, 1, 0)) %>%
  group_by(n, r2, model) %>%
  summarize(thr = mean(Hi), .groups = "drop") %>%
  ggplot(aes(x = n, y = thr, col = model)) +
  geom_line() +
  facet_wrap(~r2, labeller = label_parsed) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  labs(y = "Hypothesis selection rates",
       x = "Sample size",
       title = "Individual study true hypothesis selection rate")

output %>%
  group_by(nsim, n, r2) %>%
  summarize(bf_h1 = prod(bf_h1), .groups = "drop") %>%
  ggplot(aes(x = as.factor(n), 
             y = log(bf_h1), 
             fill = as.factor(n))) +
  geom_boxplot() +
  geom_hline(yintercept = 0, col = "grey", size = 1) +
  facet_wrap(~r2, labeller = label_parsed) +
  scale_fill_brewer(palette = "Set2") +
  theme_minimal() +
  labs(y = expression(log~BF["H"["i,u"]]),
       x = "Sample size",
       title = "Combined Bayes Factor") +
  theme(legend.position = "none")

output %>%
  mutate(bf_u = map(bf_u, ~as_tibble(matrix(.x,
                                            ncol = 3,
                                            dimnames = list(NULL,
                                                            hypnames))))) %>%
  unnest(bf_u) %>%
  group_by(nsim, n, r2) %>%
  summarise(across(c(Hi, Complement, Unconstrained), prod), .groups = "drop") %>%
  mutate(Hi = ifelse(Hi > Unconstrained, 1, 0),
         Unconstrained = ifelse(Unconstrained > Hi, 1, 0)) %>%
  group_by(n, r2) %>%
  summarize(thr = mean(Hi), .groups = "drop") %>%
  ggplot(aes(x = n, y = thr, col = r2)) +
  geom_line() +
  scale_color_brewer(palette = "Set1", labels = scales::parse_format()) +
  theme_minimal() +
  labs(y = "True hypothesis rate",
       x = "Sample size",
       title = "True hypothesis rate of hypothesis of interest versus unconstrained")
```

# Simulation 5

Simulation 5 is exactly similar to simulations 3 and 4, except that now $\beta_1, \beta_2, \beta_3$ are combined into a single variable that is the __mean__, rather than the sum, of the three separate variables. Hence, the hypothesis of interest was
$$
H_i: \beta_{mean} > 0, 
$$
evaluated against
$$
H_u: \beta_{mean}, \beta_4, \beta_5.
$$

```{r, include = F}
rm(list = ls())
load("../simulations/05_combined_variable_mean.RData")
```

```{r}
output <- output %>%
  mutate(bf_u  = map(fit,  ~c(.x[,7], unconstrained = 1)),
         bf_h1 = map_dbl(bf_u, ~.x[1]),
         pmp_u = map(bf_u, ~.x / sum(.x)),
         r2 = paste0("R^2: ", r2))

output %>%
  group_by(n, r2, model) %>%
  summarize(bf_h1 = mean(bf_h1), .groups = "drop") %>%
  ggplot(mapping = aes(x = n, y = bf_h1, col = model)) +
  geom_line() +
  geom_hline(yintercept = 1, col = "grey", size = 1) +
  scale_color_brewer(palette = "Set1") +
  facet_wrap(~r2, labeller = label_parsed) +
  theme_minimal() +
  labs(y = expression(BF["H"["i,u"]]),
       x = "Sample size",
       title = "Individual study Bayes Factor")

hypnames <- c("Hi", "Complement", "Unconstrained")

output %>%
  mutate(bf_u = map(bf_u, ~as_tibble(matrix(.x, 
                                            ncol = 3, 
                                            dimnames = list(NULL, 
                                                            hypnames))))) %>%
  unnest(bf_u) %>%
  mutate(Hi = ifelse(Hi > Unconstrained, 1, 0)) %>%
  group_by(n, r2, model) %>%
  summarize(thr = mean(Hi), .groups = "drop") %>%
  ggplot(aes(x = n, y = thr, col = model)) +
  geom_line() +
  facet_wrap(~r2, labeller = label_parsed) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  labs(y = "Hypothesis selection rates",
       x = "Sample size",
       title = "Individual study true hypothesis selection rate")

output %>%
  group_by(nsim, n, r2) %>%
  summarize(bf_h1 = prod(bf_h1), .groups = "drop") %>%
  ggplot(aes(x = as.factor(n), 
             y = log(bf_h1), 
             fill = as.factor(n))) +
  geom_boxplot() +
  geom_hline(yintercept = 0, col = "grey", size = 1) +
  facet_wrap(~r2, labeller = label_parsed) +
  scale_fill_brewer(palette = "Set2") +
  theme_minimal() +
  labs(y = expression(log~BF["H"["i,u"]]),
       x = "Sample size",
       title = "Combined Bayes Factor") +
  theme(legend.position = "none")

output %>%
  mutate(bf_u = map(bf_u, ~as_tibble(matrix(.x,
                                            ncol = 3,
                                            dimnames = list(NULL,
                                                            hypnames))))) %>%
  unnest(bf_u) %>%
  group_by(nsim, n, r2) %>%
  summarise(across(c(Hi, Complement, Unconstrained), prod), .groups = "drop") %>%
  mutate(Hi = ifelse(Hi > Unconstrained, 1, 0),
         Unconstrained = ifelse(Unconstrained > Hi, 1, 0)) %>%
  group_by(n, r2) %>%
  summarize(thr = mean(Hi), .groups = "drop") %>%
  ggplot(aes(x = n, y = thr, col = r2)) +
  geom_line() +
  scale_color_brewer(palette = "Set1", labels = scales::parse_format()) +
  theme_minimal() +
  labs(y = "True hypothesis rate",
       x = "Sample size",
       title = "True hypothesis rate of hypothesis of interest versus unconstrained")
```

# Simulation 6

In simulation 6, the set-up is fairly similar to simulation 1, except that now the number of predictors equals $k = 2$, with a correlation of $\rho = 0.3$ and a sample size of $n \in \{50, 100, 200, 400, 800\}$. The ratio of regression coefficients here equals $\beta_2 = 2\beta_1$. This situation is adjusted in a second scenario in which $X_2$ is split up in three distinct categories with cut-offs $`r levels(cut(rnorm(1000), qnorm(c(0, 1/3, 2/3, 1))))`$, resulting in an $\beta_{intercept}, \beta_{2D2}, \beta_{2D3}$. Since the smallest group $n = 25$ resulted in complete separation in some datasets, I excluded this sample size.


```{r, include = F}
rm(list = ls())
load("../simulations/06_dummied_variable.RData")
```


## Single continuous variable


```{r}
output_c <- output_c %>%
  mutate(bf_u  = map(fit,  ~c(.x[,7], unconstrained = 1)),
         bf_h1 = map_dbl(bf_u, ~.x[1]),
         pmp_u = map(bf_u, ~.x / sum(.x)),
         r2 = paste0("R^2: ", r2))


output_c %>%
  group_by(n, r2, model) %>%
  summarize(bf_h1 = mean(bf_h1), .groups = "drop") %>%
  ggplot(mapping = aes(x = n, y = bf_h1, col = model)) +
  geom_line() +
  geom_hline(yintercept = 1, col = "grey", size = 1) +
  scale_color_brewer(palette = "Set1") +
  facet_wrap(~r2, labeller = label_parsed) +
  theme_minimal() +
  labs(y = expression(BF["H"["i,u"]]),
       x = "Sample size",
       title = "Individual study Bayes Factor")

hypnames <- c("Hi", "Complement", "Unconstrained")

output_c %>%
  mutate(bf_u = map(bf_u, ~as_tibble(matrix(.x, 
                                            ncol = 3, 
                                            dimnames = list(NULL, 
                                                            hypnames))))) %>%
  unnest(bf_u) %>%
  mutate(Hi = ifelse(Hi > Unconstrained, 1, 0)) %>%
  group_by(n, r2, model) %>%
  summarize(thr = mean(Hi), .groups = "drop") %>%
  ggplot(aes(x = n, y = thr, col = model)) +
  geom_line() +
  facet_wrap(~r2, labeller = label_parsed) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  labs(y = "Hypothesis selection rates",
       x = "Sample size",
       title = "Individual study true hypothesis selection rate")

output_c %>%
  group_by(nsim, n, r2) %>%
  summarize(bf_h1 = prod(bf_h1), .groups = "drop") %>%
  ggplot(aes(x = as.factor(n), 
             y = log(bf_h1), 
             fill = as.factor(n))) +
  geom_boxplot() +
  geom_hline(yintercept = 0, col = "grey", size = 1) +
  facet_wrap(~r2, labeller = label_parsed) +
  scale_fill_brewer(palette = "Set2") +
  theme_minimal() +
  labs(y = expression(log~BF["H"["i,u"]]),
       x = "Sample size",
       title = "Combined Bayes Factor") +
  theme(legend.position = "none")

output_c %>%
  mutate(bf_u = map(bf_u, ~as_tibble(matrix(.x,
                                            ncol = 3,
                                            dimnames = list(NULL,
                                                            hypnames))))) %>%
  unnest(bf_u) %>%
  group_by(nsim, n, r2) %>%
  summarise(across(c(Hi, Complement, Unconstrained), prod), .groups = "drop") %>%
  mutate(Hi = ifelse(Hi > Unconstrained, 1, 0),
         Unconstrained = ifelse(Unconstrained > Hi, 1, 0)) %>%
  group_by(n, r2) %>%
  summarize(thr = mean(Hi), .groups = "drop") %>%
  ggplot(aes(x = n, y = thr, col = r2)) +
  geom_line() +
  scale_color_brewer(palette = "Set1", labels = scales::parse_format()) +
  theme_minimal() +
  labs(y = "True hypothesis rate",
       x = "Sample size",
       title = "True hypothesis rate of hypothesis of interest versus unconstrained")
```



## Continuous variable split into dummies


```{r}
output_d <- output_d %>%
  mutate(bf_u  = map(fit,  ~c(.x[,7], unconstrained = 1)),
         bf_h1 = map_dbl(bf_u, ~.x[1]),
         pmp_u = map(bf_u, ~.x / sum(.x)),
         r2 = paste0("R^2: ", r2))

output_d %>%
  group_by(n, r2, model) %>%
  summarize(bf_h1 = mean(bf_h1), .groups = "drop") %>%
  ggplot(mapping = aes(x = n, y = bf_h1, col = model)) +
  geom_line() +
  geom_hline(yintercept = 1, col = "grey", size = 1) +
  scale_color_brewer(palette = "Set1") +
  facet_wrap(~r2, labeller = label_parsed) +
  theme_minimal() +
  labs(y = expression(BF["H"["i,u"]]),
       x = "Sample size",
       title = "Individual study Bayes Factor")

hypnames <- c("Hi", "Complement", "Unconstrained")

output_d %>%
  mutate(bf_u = map(bf_u, ~as_tibble(matrix(.x, 
                                            ncol = 3, 
                                            dimnames = list(NULL, 
                                                            hypnames))))) %>%
  unnest(bf_u) %>%
  mutate(Hi = ifelse(Hi > Unconstrained, 1, 0)) %>%
  group_by(n, r2, model) %>%
  summarize(thr = mean(Hi), .groups = "drop") %>%
  ggplot(aes(x = n, y = thr, col = model)) +
  geom_line() +
  facet_wrap(~r2, labeller = label_parsed) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  labs(y = "Hypothesis selection rates",
       x = "Sample size",
       title = "Individual study true hypothesis selection rate")

output_d %>%
  group_by(nsim, n, r2) %>%
  summarize(bf_h1 = prod(bf_h1), .groups = "drop") %>%
  ggplot(aes(x = as.factor(n), 
             y = log(bf_h1), 
             fill = as.factor(n))) +
  geom_boxplot() +
  geom_hline(yintercept = 0, col = "grey", size = 1) +
  facet_wrap(~r2, labeller = label_parsed) +
  scale_fill_brewer(palette = "Set2") +
  theme_minimal() +
  labs(y = expression(log~BF["H"["i,u"]]),
       x = "Sample size",
       title = "Combined Bayes Factor") +
  theme(legend.position = "none")

output_d %>%
  mutate(bf_u = map(bf_u, ~as_tibble(matrix(.x,
                                            ncol = 3,
                                            dimnames = list(NULL,
                                                            hypnames))))) %>%
  unnest(bf_u) %>%
  group_by(nsim, n, r2) %>%
  summarise(across(c(Hi, Complement, Unconstrained), prod), .groups = "drop") %>%
  mutate(Hi = ifelse(Hi > Unconstrained, 1, 0),
         Unconstrained = ifelse(Unconstrained > Hi, 1, 0)) %>%
  group_by(n, r2) %>%
  summarize(thr = mean(Hi), .groups = "drop") %>%
  ggplot(aes(x = n, y = thr, col = r2)) +
  geom_line() +
  scale_color_brewer(palette = "Set1", labels = scales::parse_format()) +
  theme_minimal() +
  labs(y = "True hypothesis rate",
       x = "Sample size",
       title = "True hypothesis rate of hypothesis of interest versus unconstrained")
```

